The Ranked Nearest Neighbour Interchange space

### 2019-05-01 paper.tex
prove diameter RNNI

\begin{conjecture}
	There are two caterpillar trees in $\rnniu$ with distance $\frac{1}{2}n^2-\frac{3}{2}n+1$.
	\label{conj:caterpillar_diameter}
\end{conjecture}

% This can be computationally proven for up to $8$ taxa.

\begin{proof}
	Consider trees $(( \dots (n,1)2)\dots)n-1)$ and $(( \dots (n,n-1)n-2)\dots)1)$ and apply Lemma~\ref{lemma:caterpillar_subset_convex} and use Bubble Sort.
\end{proof}

>>>>

\begin{lemma}
	There are two caterpillar trees in $\rnniu$ with distance $\frac{1}{2}n^2-\frac{3}{2}n+1$.
	\label{conj:caterpillar_diameter}
\end{lemma}

\begin{proof}
    For this proof we will give two caterpillar trees $T_1$ and $T_2$ on $n$ taxa with $d_{RNNI}(T_1,T_2) = \frac{1}{2}n^2-\frac{3}{2}n+1$.
    \todo{$d$ or $d_{RNNI}$?}
	Let $T_1 = (( \dots (n,1)2)\dots)n-1)$ and $T_2 = (( \dots (n,n-1)n-2)\dots)1)$.
    According to Lemma~\ref{lemma:caterpillar_subset_convex}, there is a shortest path between $T_1$ and $T_2$ that only consists of caterpillar trees.
    We can compute such a shortest caterpillar path by using a modified version of Bubble Sort.
    \todo{Explain how to use Bubble Sort}
    When running this algorithm on $T_1$ and $T_2$ there are $n-1-i$ swaps of taxon $i$ with its right neighbour.
    Therefore, the total number of these swaps, and therefore $d_{RNNI}(T_1,T_2)$, is $\sum\limits_{i=1}^{n-1}(n-1-i) = \sum\limits_{i=0}^{n-2}i = \frac{1}{2}n^2-\frac{3}{2}n+1$
\end{proof}
